\huge Unnecessarily Complicated Research Title

### 2017-02-22 Literature Review/NewAFPoster.tex
Poster things
Added new file and template, if you could add in the stuff and text you
think is pertinent then that is great. I couldn't get the smartdiagram
to work with the beamerposter package, so we will need to find another
way to do it. Also the attenuation of text is necessary

\author{Tigany Zarrouk \& Mattia Gaggi } % Author(s)

@@

\begin{enumerate}
\item Replicate original model of Atrial Fibrillation (AF) from Christensen \emph{et al.}
\item Incorporate restitution of heart cells into the model. 
\item Model on more realistic morphology via translating model onto a sphere and adding restitution. 
\item Analyse to see if there is enhanced risk with the new model, using new morphology and model basis, to create a more accurate AF model.
\end{enumerate}

@@

%\begin{frame}
%\smartdiagram[bubble diagram]{Current research,
 %Physiological \\ models, Image-Based \\ Models, \textbf{ CA Models}, antiarrhythmic \\ drugs) }
% \end{frame}
 Our research is based on expanding on the work done by Kim Christensen on CA (Cellular Automata) models \cite{Christensen}.

@@

\begin{block}{Results: Connectome}

%\centering
\begin{figure}
\includegraphics[width=0.7\linewidth]{connectome}
\caption{Hemisphere of possible connections defined on the sphere model. Each vertex corresponds to a face. Longitudinal connections are in red, transversal are in blue. Starts from a single pentagon on the icosphere and then can be seen to propagate outwards. }
\end{figure}

%\end{column}

@@

%------------------------------------------------

\begin{block}{Results: Sphere and Previous model}

%\centering
\begin{figure}
\includegraphics[width=0.8\linewidth]{combchristensenspherefib}
\caption{Figures of: Christensen \emph{et al.}'s model at times of t=1, t=60 and t=470,for a, b and c, respectively, and the sphere model at times of t=1, t=41 and t=241 for d, e and f respectively. Normal wavefront propagation seen starting from pentagonal node in the leftmost figures.In figure e, the excitation wavefront propagates around the sphere, mimicking Christensen \emph{et al.}'s model, b. On the right, chaotic, fibrillatory activity has arisen from reentry circuit spontaneously manifesting itself in c and f.}
\end{figure}

@@

In Christensen \emph{et al.}'s model, the refractory period of each muscle cell was always fixed, this is not what happens in a real heart.
In a real heart the refractory period depends on the heart beat rate and on the last time each cell it was excited. The relationship between refractory period and heart beat rate is called restitution.
\end{block}

@@

%\centering
\begin{figure}
\includegraphics[width=0.65\linewidth]{xriskcurvesphere}
\caption{Figure of the Risk Curve of all the systems analysed. Y-axis: probablility of a realisation being in AF, x-axis: value of $\nu$, the  probability of a transversal connection between cells}
\end{figure}

@@

@@

%\setbeamercolor{block title}{fg=black,bg=orange!70} % Change the block title color

%\begin{block}{Contact Information}

%\begin{itemize}
%\item Web: \href{http://www.university.edu/smithlab}{http://www.university.edu/smithlab}
%\item Email: \href{mailto:john@smith.com}{john@smith.com}
%\item Phone: +1 (000) 111 1111
%\end{itemize}

>>>>

\author{Tigany Zarrouk and Mattia Gaggi } % Author(s)

@@

\begin{enumerate}
\item Replicate original model of Atrial Fibrillation (AF) from Christensen \emph{et al.}
\item Incorporate restitution of heart cells into the model. 
\item Add more features, such as a modified connectivity, new dynamics via modelling on a sphere. 
\item Analyse to see if there is enhanced risk with the model, using new morphology and model basis, to create a more accurate AF model.
\end{enumerate}

@@

%\begin{frame}
%\smartdiagram[bubble diagram]{Current research,
% Physiological \\ models, Image-Based \\ Models, \textbf{ CA Models}, antiarrhythmic \\ drugs) }
% \end{frame}
 Our research is based on expanding on the work done by Kim Christensen on CA (Cellular Automata) models \cite{Christensen}.

@@

\end{column}

%\begin{column}{.43\textwidth} % The second subdivided column within the first main column

%\end{column}
%\end{columns} % End of the subdivision

%\begin{itemize}
%\item Curabitur sapien ligula, faucibus in feugiat quis, vestibulum a turpis.
%\begin{itemize}
%\item Phasellus quis nunc neque. Suspendisse mauris diam, suscipit non gravida in, placerat id enim. Ut nec ipsum in lectus ultrices sagittis.
%\item Ut nec ipsum in lectus ultrices sagittis.
%\item Phasellus quis nunc neque.
%\end{itemize}
%\end{itemize}

%----------------------------------------------------------------------------------------
%	METHODS
%----------------------------------------------------------------------------------------

%----------------------------------------------------------------------------------------
%	MATHEMATICAL SECTION
%----------------------------------------------------------------------------------------

@@

In Christensen \emph{et al.}'s model, the refractory period of each muscle cell was always fixed, this is not what happens in a real heart.
In a real heart the refractory period depends on the heart beat rate and on the last time each cell it was excited. The relationship between refractory period and heart beat rate is called restitution.
\\
In the first part of our project, we implemented restitution in Kim Christensen model in order

@@

@@

%\centering
\begin{figure}
\includegraphics[width=0.8\linewidth]{xriskcurvesphere}
\caption{Figure of the Risk Curve of all the systems analysed. Y-axis: probablility of a realisation being in AF, x-axis: value of $\nu$, the  probability of a transversal connection between cells}
\end{figure}

@@

\end{block}
%\begin{block}{References}

%\nocite{*} % Insert publications even if they are not cited in the poster%
%%\small{\bibliographystyle{unsrt}
%\bibliography{sample}}

%\begin{frame}[allowframebreaks]

% \frametitle<presentation>{Further Reading}

%\begin{thebibliography}{1}  
  % \beamertemplatearticlebibitems
 %\bibitem{Christensen}
%\newblock Christensen \emph{et al.}, 
%\newblock \emph{Simple Model To Identify Critical Regions in Atrial Fibrillation}
%Phys. Rev. Lett. 114, 028104

  %\end{thebibliography}
%\end{frame}

%----------------------------------------------------------------------------------------
%	ACKNOWLEDGEMENTS
%----------------------------------------------------------------------------------------

\begin{block}{Acknowledgments}

\begin{itemize}
\item Thanks to Professor Kim Christensen with his guidance througout the research project. 
\end{itemize}

@@

\setbeamercolor{block title}{fg=black,bg=orange!70} % Change the block title color

\begin{block}{Contact Information}

\begin{itemize}

\item Email: \href{mailto:john@smith.com}{john@smith.com}
\item Phone: +1 (000) 111 1111
\end{itemize}

### 2017-02-22 Literature Review/conference_poster_2.tex
Poster things
Added new file and template, if you could add in the stuff and text you
think is pertinent then that is great. I couldn't get the smartdiagram
to work with the beamerposter package, so we will need to find another
way to do it. Also the attenuation of text is necessary

\usepackage{smartdiagram}
\usepackage{metalogo}
\usepackage{dtklogos}

@@

\title{\huge A Sphere Model for Atrial Fibrillation} % Poster title

\author{Tigany Zarrouk and Mattia Gaggi } % Author(s)

\institute{Supervisor: Kim Christensen.  Condensed Matter Theory Group---Imperial College London} % Institution(s)

@@

\newcommand{\leftfoot}{} % Left footer text

\newcommand{\rightfoot}{} % Right footer text

@@

\begin{enumerate}
\item Replicate original model of Atrial Fibrillation (AF) from Christensen \emph{et al.}
\item Incorporate restitution of heart cells into the model. 
\item Add more features, such as a modified connectivity, new dynamics via modelling on a sphere. 
\item Analyse to see if there is enhanced risk with the model, using new morphology and model basis, to create a more accurate AF model.
\end{enumerate}

@@

\begin{itemize}
\item Atrial Fibrillation (AF) is a type of cardiac arrhythmia and one of the major causes of stroke and heart failure. AF is also the most widespread cardiac condition, with over 30 millions of people worldwide suffering from it. In the UK, expenses related to this disease account for more than $1\%$ of the total budget of the National Health Service, which is more than $800$ million pounds. Atrial fibrillation usually manifests itself in patients affected through alterations of the normal cardiac rhythm lasting short periods of time (also called fibrillation episodes).\\
\end{itemize}

@@

\begin{block}{Phenomenology of Atrial Fibrillation}

	\begin{itemize}
	\item Each heart beat originates as an electric signal in the sinoatrial (SA) node that propagates first into the atria, then through the atrioventricular (AV) node, through Purkinje fibres 		and finally from the ventricular endocardium to the ventricular epicardium. The electric signal is conducted in the cardiac muscle cells thanks to the polarisation mechanism of the cell 		membrane.

	\item When the electric impulse propagates a single muscle cell goes through three stages:

		\begin{itemize}
 		 \item \textit{Excitable state}: the muscle cell is at rest with a negative built up potential.

  		\item \textit{Excited state}: the muscle cell is excited by its excited neighbours and the Voltage of the cell is at its peak. 
  		\item \textit{Refractory state} :the muscle cell goes through a phase during which it can't be excited again - this period is called \textit{refractory period)}.
		\end{itemize}

	\item Where the refractory period depends on the last time a cell was excited and is always fixed to a constant.\\

	\item AF is correlated to the amount of \textbf{ fibrosis} in the cardiac tissue which generates a process called reentry. \\
	During reentry the electric signal wavefront propagation breaks. It has been shown a clear link between fibrosis and AF
	Even though many treatments have been developed, the mechanisms behind this condition are not completely understood and AF remains a major topic in medical research. \\
	The current research revolves around three possible approaches:
	\end{itemize}

%\begin{frame}
%\smartdiagram[bubble diagram]{Current research,
% Physiological \\ models, Image-Based \\ Models, \textbf{ CA Models}, antiarrhythmic \\ drugs) }
% \end{frame}
 Our research is based on expanding on the work done by Kim Christensen on CA (Cellular Automata) models \cite{Christensen}.

@@

\end{column}

%\begin{column}{.43\textwidth} % The second subdivided column within the first main column

%\end{column}
%\end{columns} % End of the subdivision

%\begin{itemize}
%\item Curabitur sapien ligula, faucibus in feugiat quis, vestibulum a turpis.
%\begin{itemize}
%\item Phasellus quis nunc neque. Suspendisse mauris diam, suscipit non gravida in, placerat id enim. Ut nec ipsum in lectus ultrices sagittis.
%\item Ut nec ipsum in lectus ultrices sagittis.
%\item Phasellus quis nunc neque.
%\end{itemize}
%\end{itemize}

%\end{block}

@@

@@

@@

\begin{block}{Implementing Restitution }

In Christensen \emph{et al.}'s model, the refractory period of each muscle cell was always fixed, this is not what happens in a real heart.
In a real heart the refractory period depends on the heart beat rate and on the last time each cell it was excited. The relationship between refractory period and heart beat rate is called restitution.
\\
In the first part of our project, we implemented restitution in Kim Christensen model in order

@@

\begin{block}{Model on a Sphere}

\begin{itemize}
\item In research by Fedotov, a cellular automaton model was constructed on the surface of a triangulated sphere to model spiral rotor waves on a closed, heterogeneous surface \cite{Fedotov}. It was shown that both a decrease in refractory period and conduction velocity from a "healthy" myocardium state, where no irregular excitation waves above 300bpm are observed, resulted in an area where spiral waves were formed. In addition, a multi-electrode system was created to study the localization of AF sources by simulated electrograms. 
\end{itemize}

\end{block}
%------------------------------------------------

@@

%\centering
\begin{figure}
\includegraphics[width=0.8\linewidth]{xriskcurvesphere}
\caption{Figure of the Risk Curve of all the systems analysed. Y-axis: probablility of a realisation being in AF, x-axis: value of $\nu$, the  probability of a transversal connection between cells}
\end{figure}

@@

\begin{block}{Conclusion}
\begin{itemize}
\item A simplified mechanism of AF had been achieved by Christensen \emph{et al.'s} model through the modelling of heart muscle fibre connectivity while incorporating the effects of fibrosis. This model was improved upon by the additon of the restitution process, making AF more risky. By translating the model to a sphere, the steady growth of heart muscle fibres from the sino-atrial node could be replicated, while simulating a more realisitc morphology of the atria. The risk of AF was seen to be higher, than with the original model. Verification of this model can be achieved with the analysis of the proportion of fibrosis in atrial heart tissue. 
\end{itemize}
\end{block}

@@

\nocite{*} % Insert publications even if they are not cited in the poster
\small{\bibliographystyle{unsrt}
\bibliography{sample1}}

\end{block}
%\begin{block}{References}

%\nocite{*} % Insert publications even if they are not cited in the poster%
%%\small{\bibliographystyle{unsrt}
%\bibliography{sample}}

%\begin{frame}[allowframebreaks]

% \frametitle<presentation>{Further Reading}

%\begin{thebibliography}{1}  
  % \beamertemplatearticlebibitems
 %\bibitem{Christensen}
%\newblock Christensen \emph{et al.}, 
%\newblock \emph{Simple Model To Identify Critical Regions in Atrial Fibrillation}
%Phys. Rev. Lett. 114, 028104

  %\end{thebibliography}
%\end{frame}

%\end{block}

@@

\begin{itemize}
\item Thanks to Professor Kim Christensen with his guidance througout the research project. 
\end{itemize}

@@

\begin{itemize}

\item Email: \href{mailto:john@smith.com}{john@smith.com}
\item Phone: +1 (000) 111 1111
\end{itemize}

>>>>

@@

\title{\huge Unnecessarily Complicated Research Title} % Poster title

\author{John Smith, James Smith and Jane Smith} % Author(s)

\institute{Department and University Name} % Institution(s)

@@

\newcommand{\leftfoot}{http://www.LaTeXTemplates.com} % Left footer text

\newcommand{\rightfoot}{john@smith.com} % Right footer text

@@

\begin{enumerate}
\item Donec fringilla, velit id lobortis commodo, eros dui consectetur mi, ut interdum lorem dui sed mauris.
\item Nulla ac nulla rhoncus est bibendum ullamcorper:
\item Quisque vestibulum, nisl sit amet gravida ultricies dis parturient montes, nascetur ridiculus musobortis commodo, eros dui consectetur mi.
\end{enumerate}

@@

\begin{itemize}
\item Donec fringilla, velit id lobortis commodo, eros dui consectetur mi, ut interdum lorem dui sed mauris. Duis id sem nunc, a pharetra odio. Phasellus posuere \alert{semper massa}, id bibendum ligula tristique at. Integer sit amet vulputate turpis. Sed erat lacus, faucibus at viverra et, mattis nec sem. Cras faucibus \alert{scelerisque} cursus. Opet volutpat ligula. Duis semper lorem eget dui dignissim porttitor. Nulla facilisi. In ullamcorper lorem quis dolor iaculis nec egestas enim ultricies. Cras ut mauris elit, ut lacinia dui. Proin in ante et libero hendrerit iaculis. Nulla eu erat a urna laoreet auctor id a turpis. Nam mollis tristique neque eu luctus. Suspendisse rutrum congue nisi sed convallis. Aenean id neque dolor.
\end{itemize}

@@

%----------------------------------------------------------------------------------------
%	MATERIALS
%----------------------------------------------------------------------------------------

\begin{block}{Materials}

\begin{columns} % Subdivide the first main column
\begin{column}{.54\textwidth} % The first subdivided column within the first main column
\begin{itemize}
\item Vestibulum nisl, quis euismod velit eros in ligula.
\begin{itemize}
\item Cras rhoncus quam et augue convallis in elementum urna tincidunt.
\end{itemize}
\item Proin ut vestibulum augue.
\begin{itemize}
\item Donec dapibus sagittis neque eu ultrices.
\end{itemize}
\end{itemize}
\end{column}

\begin{column}{.43\textwidth} % The second subdivided column within the first main column
\centering
\begin{figure}
\includegraphics[width=0.8\linewidth]{placeholder.jpg}
\caption{Figure caption}
\end{figure}
\end{column}
\end{columns} % End of the subdivision

\begin{itemize}
\item Curabitur sapien ligula, faucibus in feugiat quis, vestibulum a turpis.
\begin{itemize}
\item Phasellus quis nunc neque. Suspendisse mauris diam, suscipit non gravida in, placerat id enim. Ut nec ipsum in lectus ultrices sagittis.
\item Ut nec ipsum in lectus ultrices sagittis.
\item Phasellus quis nunc neque.
\end{itemize}
\end{itemize}

@@

@@

\begin{block}{Methods}

\begin{itemize}
\item Maecenas Vel Nisl Elit
\begin{itemize}
\item Suspendisse potenti. Fusce a est eget turpis rhoncus varius sed sed dui. Cras justo nibh, bibendum a cursus eget, consequat et dui. Maecenas vel nisl elit, sed dignissim dolor. 
\item In hac habitasse platea dictumst.
\end{itemize}

\item Viewpoint Matching Constraints
\begin{itemize}
\item Cum sociis natoque penatibus et magnis dis parturient montes, nascetur ridiculus mus. 
\item Proin in nisi diam.
\item Nam ultricies pellentesque nunc, ultrices volutpat nisl ultrices a.
\end{itemize}

\item Volutpat 
\begin{itemize}
\item Duis semper lorem eget dui dignissim porttitor.
\item Nulla facilisi. In ullamcorper lorem quis dolor.
\end{itemize}
\end{itemize}

@@

\begin{block}{Mathematical Section}

\begin{itemize}
\item Maecenas Ultricies Feugiat Velit Non Mattis.
\begin{itemize}
\item Duis ante erat, bibendum nec tempus nec, interdum quis est. Nulla at mollis tortor. Phasellus quis leo dolor, aliquam laoreet orci $X$ Donec dapibus sagittis neque eu nec, interdum quis est. $Y_n, n=1,\cdots,N$ ndum nec tempus nec, interd
\begin{align*}
X \rightarrow r(X) & = \arg \max_{c} \Big\{ \max_n \big\{ \sum_{x_i \in X} \delta(x_i,Y_{n,c})\big\} \Big\} 
\end{align*}
\item Cras faucibus scelerisque cursus. Proin ut vestibulum augue. $\delta(x_i,Y_{n,c})$
\end{itemize}
\item Fusce tempus arcu id ligula varius dictum. Donec ut nisl dui, ac consectetur elit. In nec enim porta augue venenatis sollicitudin. Phasellus quis nunc neque. Suspendisse mauris diam, suscipit non gravida in, placerat id enim. Ut nec ipsum in lectus ultrices sagittis.
\end{itemize}

@@

\begin{block}{Results: Table}

\begin{itemize}
\item Ased Aliquet Luctus Lectus
\end{itemize}

\begin{table}
\begin{tabular}{l l l}
\toprule
\textbf{Treatments} & \textbf{Response 1} & \textbf{Response 2}\\
\midrule
Treatment 1 & 0.0003262 & 0.562 \\
Treatment 2 & 0.0015681 & 0.910 \\
Treatment 3 & 0.0009271 & 0.296 \\
\bottomrule
\end{tabular}
\caption{Table caption}
\end{table}

\begin{itemize}
\item Sollicitudin Vel Orci
\item Maecenas Ultricies Feugiat Velit Non Mattis.
\end{itemize}

\begin{table}
\begin{tabular}{l l l}
\toprule
\textbf{Treatments} & \textbf{Response 1} & \textbf{Response 2}\\
\midrule
Treatment 1 & 0.0003262 & 0.562 \\
Treatment 2 & 0.0015681 & 0.910 \\
Treatment 3 & 0.0009271 & 0.296 \\
\bottomrule
\end{tabular}
\caption{Table caption}
\end{table}

@@

%------------------------------------------------

@@

\begin{figure}
\includegraphics[width=0.8\linewidth]{placeholder.jpg}
\caption{Figure caption}
\end{figure}

@@

\begin{block}{Conclusion}

\begin{itemize}
\item Opet volutpat ligula. Duis semper lorem eget dui dignissim porttitor. Nulla facilisi. In ullamcorper lorem quis dolor iaculis nec egestas enim ultricies. Cras ut mauris elit, ut lacinia dui. Proin in ante et libero hendrerit iaculis.
\item Nulla eu erat a urna laoreet auctor id a turpis. Nam mollis tristique neque eu luctus. Suspendisse rutrum congue nisi sed convallis. 
\item Aenean id neque dolor.
\item Opet volutpat ligula. Duis semper lorem eget dui dignissim porttitor. Nulla facilisi. In ullamcorper lorem quis dolor iaculis nec egestas enim ultricies. Cras ut mauris elit, ut lacinia dui. Proin in ante et libero hendrerit iaculis.
\end{itemize}

@@

\nocite{*} % Insert publications even if they are not cited in the poster
\small{\bibliographystyle{unsrt}
\bibliography{sample}}

@@

\begin{itemize}
\item Nam mollis tristique neque eu luctus. Suspendisse rutrum congue nisi sed convallis. Aenean id neque dolor. Pellentesque habitant morbi tristique senectus et netus et malesuada fames ac turpis egestas.
\end{itemize}

@@

\begin{itemize}
\item Web: \href{http://www.university.edu/smithlab}{http://www.university.edu/smithlab}
\item Email: \href{mailto:john@smith.com}{john@smith.com}
\item Phone: +1 (000) 111 1111
\end{itemize}

### 2017-02-22 Literature Review/somedraft2.tex
Poster things
Added new file and template, if you could add in the stuff and text you
think is pertinent then that is great. I couldn't get the smartdiagram
to work with the beamerposter package, so we will need to find another
way to do it. Also the attenuation of text is necessary

%\begin{frame}
%\smartdiagram[bubble diagram]{Current research,
% Physiological \\ models, Image-Based \\ Models, \textbf{ CA Models}, antiarrhythmic \\ drugs) }
% \end{frame}
 Our research is based on expanding on the work done by Kim Christensen on CA (Cellular Automata) models \cite{Christensen}.

@@

%\end{column}
%\end{columns} % End of the subdivision

@@

\begin{itemize}
\item In research by Fedotov, a cellular automaton model was constructed on the surface of a triangulated sphere to model spiral rotor waves on a closed, heterogeneous surface \cite{Fedotov}. It was shown that both a decrease in refractory period and conduction velocity from a "healthy" myocardium state, where no irregular excitation waves above 300bpm are observed, resulted in an area where spiral waves were formed. In addition, a multi-electrode system was created to study the localization of AF sources by simulated electrograms. 
\end{itemize}

@@

\begin{block}{Conclusion}
\begin{itemize}
\item A simplified mechanism of AF had been achieved by Christensen \emph{et al.'s} model through the modelling of heart muscle fibre connectivity while incorporating the effects of fibrosis. This model was improved upon by the additon of the restitution process, making AF more risky. By translating the model to a sphere, the steady growth of heart muscle fibres from the sino-atrial node could be replicated, while simulating a more realisitc morphology of the atria. The risk of AF was seen to be higher, than with the original model. Verification of this model can be achieved with the analysis of the proportion of fibrosis in atrial heart tissue. 
\end{itemize}
\end{block}

>>>>

%\smartdiagram[bubble diagram]{Current research,
% Physiological \\ models, Image-Based \\ Models, \textbf{ CA Models}, antiarrhythmic \\ drugs) }

 %Our research is based on expanding on the work done by Kim Christensen on CA (Cellular Automata) models \cite{Christensen}.

@@

%\end{column}
\end{columns} % End of the subdivision

@@

\begin{itemize}
In research by Fedotov, a cellular automaton model was constructed on the surface of a triangulated sphere to model spiral rotor waves on a closed, heterogeneous surface \cite{Fedotov}. It was shown that both a decrease in refractory period and conduction velocity from a "healthy" myocardium state, where no irregular excitation waves above 300bpm are observed, resulted in an area where spiral waves were formed. In addition, a multi-electrode system was created to study the localization of AF sources by simulated electrograms. 
\end{itemize}

@@

\begin{block}{Conclusion}
\begin{itemize}
A simplified mechanism of AF had been achieved by Christensen \emph{et al.'s} model through the modelling of heart muscle fibre connectivity while incorporating the effects of fibrosis. This model was improved upon by the additon of the restitution process, making AF more risky. By translating the model to a sphere, the steady growth of heart muscle fibres from the sino-atrial node could be replicated, while simulating a more realisitc morphology of the atria. The risk of AF was seen to be higher, than with the original model. Verification of this model can be achieved with the analysis of the proportion of fibrosis in atrial heart tissue. 
\end{itemize}
\end{block}
